\huge A Usability Evaluation of Tor Launcher

### 2017-03-15 pets2017-paper/pets2017-paper.tex
Unsplit sentence per shepherd's comment.

Our changes significantly increased success rates (one-tailed Pearson's chi-square test ; $\chi^2 = 2.808$, $\mbox{df} = 1$, $p < 0.047$, albeit with small effect size $\phi=0.157$), helping users connect to Tor.

>>>>

Our changes significantly increased success rates (one-tailed Pearson's chi-square test; $\chi^2 = 2.808$, $\mbox{df} = 1$, $p < 0.047$, albeit with small effect size $\phi=0.157$).
